No Replication Without Process Documentation:  An Assessment of Management

### 2020-03-26 R/MSE manuscript.Rmd
update text of the abstract and introduction

---
title: 'No Replication Without Process Documentation:  An Assessment of Management
  Strategy Evaluations'
author:
- affiliation: School for Marine Science and Technology, University of Massachusetts
    - Dartmouth
  name: Jonathan W. Cummings, Amanda Hart, Gavin Fay
output:
  bookdown::html_document2:
    number_sections: false
  bookdown::word_document2:
  bookdown::pdf_document2:
    number_sections: false
always_allow_html: yes
biblio-style: apalike
endnote: no
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
header-includes: \usepackage{hyperref}
keywords: pandoc, r markdown, knitr
bibliography: MSEreview.bib
abstract: The aim and vision for fisheries management that comes from management strategy evaluation and adaptive management is a nobel and aspirational vision.  We review MSE documentation in the published literature to appraise the achievement of this vision, finding that reality doesn't fully reflect this vision. The steps taken to complete the MSE process often are not documented. Scientists often fulled the role of fishery stakeholders, seemingly selecting the objectives and alternatives to evaluate in most MSEs. Facilitators and decision analysts -- participants focused on the decision making process -- were rarely participants in MSE processes.  Conservation, Economic, and Yield focused objectives were commonly considered in MSE processes, while broader social objectives were rarely considered.  The picture painted by MSE documentation is primarily one of scientist driven simulation studies rather than management driven decision processes, with limited process documentation.
---

@@

# Introduction 
The calls for fisheries management to utilize management strategy evaluation and adaptive management have been both aspirational and estimable in their aim and vision. For example, management strategy evaluation (MSE) is "widely considered to be the most appropriate way to evaluate the trade‐offs achieved by alternative management strategies and to assess the consequences of uncertainty for achieving management goals” [@Punt]. The positive aspects of MSE that have been listed include that it is “A tool that scientists and managers can use to simulate the workings of a fisheries system and allow them to test whether potential harvest strategies—or management procedures— can achieve pre-agreed management objectives.”[@Pew], that it “can be used to identify a ‘best’ management strategy among a set of candidate strategies" [@PuntLab] and “MSE has the advantage of being able to reveal the trade-offs among a range of possible management decisions, and should assist our Commissioners in determining whether the objectives should be weighted differently. Specifically, to provide the information on which to base a rational decision, given objectives, preferences, and attitudes to risk.”  [@IPHC].  Based on these descriptions MSE is a compelling tool to support and improve fisheries management decisions.

In terms of the MSE process, it is described as being "at the interface between science and policy.” [@PuntLab] and being an “Undertaking [that] requires scientists, managers, and stakeholders to be involved throughout the process." [@IPHC] The International Pacific Halibut Commission (2017) also states, "While the scientists do the modelling, managers must offer extensive input. Because of the many steps and the iterative process, communication among parties is critical for achieving buy-in on the results of the management strategy evaluation.”

@@

### Objectives 
Our overall objectives is to determine the extent that MSE documentation can support learning within the MSE practitioner community?  Given that scientific publication is the primary means of communicating the results of MSE, we review the scientific literature to assess the extent to which the process and aims of MSE, and adaptive management are being achieved and supported by the scientific literature. To assess this we determine how MSEs utilize standard components of decision making processes. We use the structured decision making (SDM) process [@SDM] -- the decision making framework in which adaptive management occurs -- as our framework for evaluation.  Using this framework we review published MSEs to:

>>>>

---
title: 'No Replication Without Process Documentation:  An Assessment of Management
  Strategy Evaluations'
author:
- affiliation: School for Marine Science and Technology, University of Massachusetts
    - Dartmouth
  name: Jonathan W. Cummings, Amanda Hart, Gavin Fay
output:
  bookdown::html_document2:
    number_sections: false
  bookdown::word_document2:
  bookdown::pdf_document2:
    number_sections: false
always_allow_html: yes
biblio-style: apalike
endnote: no
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
header-includes: \usepackage{hyperref}
keywords: pandoc, r markdown, knitr
bibliography: MSEreview.bib
abstract: The aim and vision for fisheries management that comes from management strategy evaluation and adaptive management is a noble and aspirational vision.  We review MSE documentation in the published literature to appraise the achievement of this vision, finding that reality doesn't fully reflect this vision. The steps taken to complete the management strategy evaluation process often are not documented. Scientists often filled the role of fishery stakeholders, seemingly selecting the objectives and alternatives to evaluate in most management strategy evaluations. Facilitators and decision analysts -- participants focused on the decision making process rather than making the decision -- were rarely participants in MSE processes.  Conservation, Economic, and Yield focused objectives were commonly considered in MSE processes, while broader social objectives were rarely considered.  The picture painted by MSE documentation is primarily one of scientist driven simulation studies rather than management driven decision processes, with limited process documentation occurring. We hope providing a repository for reviews of previous management strategy evaluatons will aid and speed learning among practitioners of management strategy evaluation.
---

@@

# Introduction 
The calls for fisheries management to utilize management strategy evaluation and adaptive management have been both aspirational and estimable in their aim and vision. For example, management strategy evaluation (MSE) is "widely considered to be the most appropriate way to evaluate the trade‐offs achieved by alternative management strategies and to assess the consequences of uncertainty for achieving management goals” [@Punt]. The positive aspects of MSE that have been listed include that it is “A tool that scientists and managers can use to simulate the workings of a fisheries system and allow them to test whether potential harvest strategies — or management procedures — can achieve pre-agreed management objectives.”[@Pew], that it “can be used to identify a ‘best’ management strategy among a set of candidate strategies" [@PuntLab] and “MSE has the advantage of being able to reveal the trade-offs among a range of possible management decisions, and should assist our Commissioners in determining whether the objectives should be weighted differently. Specifically, to provide the information on which to base a rational decision, given objectives, preferences, and attitudes to risk.”  [@IPHC].  Based on these descriptions MSE is a compelling tool to support and improve fisheries management decisions.

Are the results of MSE living up to their descriptions? Are MSEs evaluating trade-offs and the consequences of uncertainty? Do they test potential harvest strategies? Were the management objectives used to evaluate management proceedures established and agreed to? Was a 'best' management strategy identified? Was consideration given to the weights on objectives, preferences, and attitudes to risk?

In the descriptions of the MSE process, the process itself is described as being "at the interface between science and policy.” [@PuntLab] and being an “Undertaking [that] requires scientists, managers, and stakeholders to be involved throughout the process." [@IPHC] The International Pacific Halibut Commission (2017) also states, "While the scientists do the modelling, managers must offer extensive input. Because of the many steps and the iterative process, communication among parties is critical for achieving buy-in on the results of the management strategy evaluation.”

ARe MSE processes being conducted in the manner described? Do MSE processes consider and account for the interface between science and policy? Are scientists, managers and stakeholders involved and communicating through and iterative process that creates buy-in?

@@

### Objectives 
Our overall objectives is to determine the extent that MSE achieves the aspirational aims outlined above, and whether MSE documentation supports learning within the MSE practitioner community.  Given that scientific publication is the primary means of communicating the results of MSE, we review the scientific literature to assess the extent to which the process and aims of MSE, and adaptive management are being achieved and supported by the scientific literature. To assess this we determine how MSEs utilize standard components of decision making processes. We use the structured decision making (SDM) process [@SDM] -- the decision making framework in which adaptive management occurs -- as our framework for evaluation.  Using this framework we review published MSEs to:
